Asteroseismology {\it sans Fourier}: soon to be crushed by DFM

### 2017-07-02 paper/paper.tex
typo

%% Mark off the abstract in the ``abstract'' environment. 
\begin{abstract}\noindent % trust the Hogg
Stellar oscillations are stochastically driven high-quality (long-coherence-time) modes.
If a star is observed through an observing campaign that is shorter
than the coherence time of a mode, that mode will effectively appear
coherent within that time interval.
Here we exploit this to create an inexpensive probabilistic model for
asteroseismology data called \bsa.
The huge advantage of \bsa\ over to traditional asteroseismology
approaches is that it does not require the performance of a fourier
transform or anything like it; this permits the measurement of
asteroseismic parameters in data sets that are irregularly or sparsely
sampled, or in data sets where the critical modes are near the edges
of the available frequency space (near the inverse exposure time at
the high-frequency end or near the inverse of the duration of the
campaign at the low-freqency end).
It also permits the construction of a tractable and justifiable
likelihood function, even when the noise processes are non-trivial.
We produce a parameterized description of an asteroseismic frequency
spectrum and use it along with this likelihood function to produce
posterior estimates of asteroseismic parameters for stars in the
\kepler\ data.
We sub-sample the \kepler\ light curves to (short duration)
\tess-like and (sparsely sampled) \gaia-like data sets and show that
even in these much smaller data sets, we ought to be able to estimate
asteroseismic parameters for many stars, and (because we are just
turning the Bayesian crank) without human intervention.
Much of what is done here could be done with Gaussian Processes; the
advantages of \bsa\ are that it is conceptually simple, and that it
has better scaling for some classes of problems.
\end{abstract}

>>>>

%% Mark off the abstract in the ``abstract'' environment. 
\begin{abstract}\noindent % trust the Hogg
Stellar oscillations are stochastically driven high-quality (long-coherence-time) modes.
If a star is observed through an observing campaign that is shorter
than the coherence time of a mode, that mode will effectively appear
coherent within that time interval.
Here we exploit this to create an inexpensive probabilistic model for
asteroseismology data called \bsa.
The huge advantage of \bsa\ over traditional asteroseismology
approaches is that it does not require the performance of a fourier
transform or anything like it; this permits the measurement of
asteroseismic parameters in data sets that are irregularly or sparsely
sampled, or in data sets where the critical modes are near the edges
of the available frequency space (near the inverse exposure time at
the high-frequency end or near the inverse of the duration of the
campaign at the low-freqency end).
It also permits the construction of a tractable and justifiable
likelihood function, even when the noise processes are non-trivial.
We produce a parameterized description of an asteroseismic frequency
spectrum and use it along with this likelihood function to produce
posterior estimates of asteroseismic parameters for stars in the
\kepler\ data.
We sub-sample the \kepler\ light curves to (short duration)
\tess-like and (sparsely sampled) \gaia-like data sets and show that
even in these much smaller data sets, we ought to be able to estimate
asteroseismic parameters for many stars, and (because we are just
turning the Bayesian crank) without human intervention.
Much of what is done here could be done with Gaussian Processes; the
advantages of \bsa\ are that it is conceptually simple, and that it
has better scaling for some classes of problems.
\end{abstract}
